### 2020-04-15 dataprep.tex
more questions

\fix{The logical 3d torus layout is $25\times 16\times 24$. How does
  the 16 dimension map onto this? Are the 4 nodes actually very far
  apart in terms of the network layout?}

@@

>>>>

\fix{In the decomissioning video, I noticed there are actually 12+2+12
  cabinets, the middle two being different. Are the compute nodes the
  pairs of outside 12s and the two middle are service nodes?}

\fix{The logical 3d torus layout is $25\times 16\times 24$. How do
  the 25 and 16 dimensions map onto this? Are the 4 nodes actually very far
  apart in terms of the network layout via the two routers?}

@@

\fix{How does the cooling water circulate?}
